### 2018-07-31 CS761-RandomizedAlgorithms/assignments/a4.tex
Think we need to fix q2 from 3n to kn

Now in the inductive step we suppose the claims holds for $x_0, \dots, x_{i-1}$ and consider $x_i$ with $i \geq 1$. Let $P$ be the augmenting path used to obtain $x_i$ from $x_{i-1}$. If $v \not\in V(P) \cup \{b\}$ then by induction the claim already holds at $v$. Further by definition the claim always holds at $b$. So it remains to verify the claim on vertices of $P$. Let $v \in V(P)\backslash\{s,t\}$. Suppose $uv, vx \in E(P)$. Then we have

@@

@@

We initialize our algorithm with integral flow $x = 0$ and 

@@

%Problem 3
\section{}

%Problem 4
\section{}

%Problem 5
\section{}

%Problem 6
\section{}
\end{document}

>>>>

Now in the inductive step we suppose the claims holds for $x_0, \dots, x_{i-1}$ and consider $x_i$ with $i \geq 1$. Let $P$ be the augmenting path used to obtain $x_i$ from $x_{i-1}$. The digraph $D'_{x_i}$ is obtained from $D'_{x_{i-1}}$ by flipping the orientation of every arc along $P$.

\paragraph{} If $v \not\in V(P) \cup \{b\}$ then by induction the claim already holds at $v$. Further by definition the claim always holds at $b$. So it remains to verify the claim on vertices of $P$. Let $v \in V(P)\backslash\{s,t\}$. Suppose $uv, vx \in E(P)$. Then we have

@@

\paragraph{Algorithm}
We initialize our algorithm with integral flow $x = 0$. Our algorithm iterates the following step until our flow $x$ has value $k$ (which it then returns). Let $w$ be the associated weighting on $D'_{x} = G + \{tb,bs\}$. Perform a random walk on $D'_x$ starting from $b$ with transition probability of arc $uv$, $P_{uv}$ equal to 
$$P_{uv} = \frac{w(uv)}{w(\delta^{out}(u))}.$$
End this random walk when you return to $b$. The walk has identified an augmenting path $P$. Augment flow of $x$ along $P$ and repeat.

@@

The expected time to find an augmenting path in any iteration is equal to $H_{b,b}$, the hitting time of $b,b$. We have that $H_{b,b} = \frac{1}{\pi_b}$ where $\pi_b$ is the probability of being in $b$ in the stationary distribution.
	Let $W_x = w(E(D'_x))$. For any $v \in V(D'_x)$, $\pi_v = \frac{w(\delta^{out}(v))}{W_x}$.
	We calculate
	$$\pi_v = \sum_{u: uv \in E(D'_x)} \pi_uP_{uv} = \sum_{u:uv \in E(D'_x)} \frac{w(\delta^{out}(u))}{W_x}\frac{w(uv)}{w(\delta^{out}(u))} = \frac{w(\delta^{in}(v))}{W_x} = \frac{w(\delta^{out}(v))}{W_x} = \pi_v$$
	with the second last equality following from out previous Claim. Since 
	$$\sum_{v \in V(D'_x)} \pi_v = \sum_{v\in V(D'_x)} \frac{w(\delta^{out}(v))}{W_x} = \frac{W_x}{W_x} = 1$$
	this is the unique stationary distribution.
From this Claim above we see that $H_{b,b} = \frac{W_x}{w(\delta^{out}(b))}$ at each iteration of the algorithm.
In iteration $i$, $w(\delta^{out}(b)) = w(bs) = k-i$ since $i$ is the value of flow $x$ in iteration $i$. Since $w(e)$ is at most $1$ for each $e$ in the edge set of $G$, and $w(e) \leq k\leq |E(G)|$ for $bs, tb$. Hence $W_x \leq 2m$ where $m = |E(G)|$. Therefore in iteration $i$,
$$H_{b,b} \leq \frac{2m}{k-i}.$$
So the total expected running time is at most
$$\sum_{i=0}^k\frac{m}{k-i} = m\log k \leq m\log m.$$
Thus the running time $\tilde{O}(|E|)$ as desired.$\blacksquare$
\newpage

@@

Consider an instance $I$ of $k$SAT with $n$ variables $x_1,\dots,x_n$ and $m$ clauses $C_1, \dots, C_m$. We solve it using the following generalization of Sch\"oning's Algorithm:
\begin{enumerate}
	\item Repeat up to $N$ times, terminating if all clauses of $I$ are satisfied:
	\begin{enumerate}
		\item Start with a random initial assignment
		\item Repeat up to $3n$ steps, terminating if all clauses satisfied: switch the value of a random variable in an unsatisfied clause.
	\end{enumerate}
	\item Return a satisfying assignment if it is found; otherwise return ``unsatisfiable".
\end{enumerate}
Let $S$ be a satisfying assignment. Let $A_i$ be the assignment in the $i$-th step of the algorithm. Let $X_i$ be the number of variables that have the same value in $A_i$ and $S$. If $X_i = n$ then $A_i = S$ and hence we are done.
We can view our algorithm as a random walk with states $0$ to $n$ denoting the value of $X_i$ when we are in that state. If we are in state $X_i$ at iteration $i$ we transition to state $X_i+1$ with probability $\frac{1}{k}$ and to state $X_i-1$ with probability $\frac{k-1}{k}$.
Suppose we have assignment $A_i$ at iteration $i$ with $j$ mismatches with $S$, i.e. $X_i = n-j$. Then we reach state $n$ in $3j$ steps provided there are $j$ steps back and $2j$ steps forward among these $3j$ steps. This happens with probability
$${3j\choose j}(\frac{k-1}{k})^j(\frac{1}{k})^{2j}.$$
This is a lower bound on reaching $n$ in $3n$ steps.
We invoke Stirling's formula:
$$\sqrt{2\pi m}\frac{m}{e}^m \leq m! \leq 2\sqrt{2\pi m}\frac{m}{e}^m$$
to obtain a better estimate. Observe
$${3j\choose j} \geq \frac{\sqrt{2\pi 3j}}{4\sqrt{2\pi 2j}\sqrt{2\pi j}}\frac{3j}{e}^{3j}\frac{e}{2j}^{2j}\frac{e}{j}^j = \frac{c}{\sqrt{j}}\frac{27}{4}^j$$
where $c = \frac{\sqrt{3}}{8\sqrt{\pi}}$ (a constant).
There our probability of reaching $n$ starting with $j$ mismatches is at least
$$\frac{c}{\sqrt{j}}\frac{27}{4}^j(\frac{k-1}{k})^j(\frac{1}{k})^{2j}$$
\newpage
%Problem 3

\newpage
%Problem 4
\section{}

\newpage
%Problem 5
\section{}

\newpage
%Problem 6
\section{}
\end{document}
